Vagueness and imprecise imitation in signaling games

### 2016-02-24 paper/version_05/paper.tex
Added reference to other identification experiments that confirm the pervasiveness of confusion and the relation with similarity.

Imitation of success, as described above, presupposes that agents make no mistakes when
observing states, or choosing interpretations. This may not always be an appropriate
assumption, especially when some states can be perceptually similar and therefore likely to be
confused for one another.
Human performance in these situations has been studied by a number of authors in experimental psychology~\citep{takane_structures_1992}.
In a stimulus identification experiment~\citep{luce_detection_1963}, subjects are presented in each trial with a stimulus to be identified out of a fixed set.
The more similar the stimuli are to each other, the larger the number of errors subjects make.
For example, in Robert Nosofsky's experiments~\citep{Nosofsky1986:Attention-Simil}, stimuli consisted of 16 semicircles with a radial line from the center to the rim, varying in size (radius of 0.478, 0.500, 0.522, or 0.544 cm) and angle of the line (50º, 53º, 56º, or 59º).
In over 9000 trials, the two subjects identified the stimulus correctly only approximately 44\% and 35\% of the time.

>>>>

Imitation of success, as described above, presupposes that agents make no mistakes when
observing states, or choosing interpretations. This may not always be an appropriate
assumption, especially when some states can be perceptually similar and therefore likely to be
confused for one another.
Human performance in these situations has been studied by a number of authors in experimental psychology. %~\citep{takane_structures_1992}.
In a stimulus identification experiment~\citep{luce_detection_1963}, subjects are presented in each trial with a stimulus to be identified out of a fixed set.
The more similar the stimuli are to each other, the larger the number of errors subjects make.
For example, in Robert Nosofsky's experiments~\citep{Nosofsky1986:Attention-Simil}, stimuli consisted of 16 semicircles with a radial line from the center to the rim, varying in size (radius of 0.478, 0.500, 0.522, or 0.544 cm) and angle of the line (50º, 53º, 56º, or 59º).
In over 9000 trials, the two subjects identified the stimulus correctly only approximately 44\% and 35\% of the time.
Similar experiments have been conducted with other identification tasks, for example, for frequency and intensity of tones, taste, hue of colors, and magnitude of lines and areas~\citep{donkin_why_2015}.
The empirical data confirms not only the pervasiveness of variation in the subjects' ability to correctly identify stimuli, but also the relation between similarity and likelihood of stimulus confusion, and further suggests that the phenomenon might extend to all types of perception.
